\section{Analysis of Database}
\label{sec:database} 
Bike-sharing rental process is highly correlated to the environmental and seasonal settings. For instance, weather conditions,
precipitation, day of week, season, hour of the day, etc. can affect the rental behaviors. The core data set is related to
the two-year historical log corresponding to years 2011 and 2012 from Capital Bikeshare system, Washington D.C., USA which is
publicly available in http://capitalbikeshare.com/system-data. We aggregated the data on two hourly and daily basis and then
extracted and added the corresponding weather and seasonal information. Weather information are extracted from http://www.freemeteo.com.

The dataset provided in file \texttt{hour.csv} consists of data fields shown in Table~\ref{tab:fields}.

\begin{table}
\small
\caption{Data fields in hour.csv}
\centering
\label{tab:fields}
\begin{tabular}{|l|l|}
  \hline
  \textbf{Fields} & \textbf{Meaning} \\\hline
  instant&Record index\\\hline
  dteday&Date\\\hline
  season & Season (1:springer, 2:summer, 3:fall, 4:winter)\\\hline
    yr & Year (0: 2011, 1:2012)\\\hline
    mnth & Month ( 1 to 12)\\\hline
	hr & Hour (0 to 23)\\\hline
	holiday & Weather day is holiday or not \\\hline
	weekday & Day of the week\\\hline
    workingday & If day is neither weekend nor holiday is 1, otherwise is 0\\\hline
	\multirow{4}*{weathersit} &
		 1: Clear, Few clouds, Partly cloudy, Partly cloudy\\
		& 2: Mist + Cloudy, Mist + Broken clouds\\
		& 3: Light Snow, Light Rain + Thunderstorm \\
		& 4: Heavy Rain + Ice Pallets + Thunderstorm + Mist\\\hline
	temp & Normalized temperature in Celsius\\\hline
	atemp& Normalized feeling temperature in Celsius\\\hline
	hum& Normalized humidity. \\\hline
	windspeed& Normalized wind speed\\\hline
	casual& Count of casual users\\\hline
	registered& Count of registered users\\\hline
	cnt& Count of total rental bikes including casual and registered\\
  \hline
\end{tabular}

\end{table}

In the previous 17 data fields, the last three fields \emph{casual}, \emph{registered} and \emph{cnt} are the responses of our model. Most of the rest fields are quantitative predictors, however there are some predictors that should be treated as qualified predictors like \emph{holiday} or \emph{weekday}; such data fields need to be preprocessed so that R language could take them as qualified predictors and create dummy variables automatically. As to the temporal fields such as \emph{season, hr, mnth}, we will initially take them as discrete variables and explore the method of transforming them into continuous variable. 